### 2009-11-27 doc/tech_doc/client/client_technical.tex
updated brokering appendix

\chapter{Broker mapping}
\label{app:broker-mapping}

This document contains a description of the broker used in the Advanced
Resource Connector (ARC) middleware as of version 1.0. In section
\ref{sec:Attribute-matching} a description of how target attributes
are matched and compared to attributes specified in the job description.

In the broker attributes published by the candidate target need to
be matched and compared to attributes specified in the job description
to be able to select targets which are suitable for accepting the
job description. Targets which do not pass a certain comparison will
be not be a candidate target for submission. Detailed information
about the attributes described below can be found in the ARC job description
document. First the broker will check some basics for the target being
processed. First, if the job description specifies submission to specific
targets and/or queues, the target will be checked and if it is not
among these targets and/or queues, it will be dropped. Next the number
of free slots on the target will be checked, and if no free slots
exist, then it will be dropped. After this, the health state of the
target is checked, and if any other value than "ok"
is published then it is dropped. Last, if middleware specific submission
is specified in the job description, the middleware type of the target
is checked, and if it does not satisfy the middleware requirements
then it is dropped. After these basic checks, certain attributes specified
in the job description are compared to the attributes published by
the target being processed. If the target does not publish a attribute
which is specified in the job description the target will dropped,
with some exceptions.

>>>>

\chapter{Broker mapping}
\label{app:broker-mapping}
The table below shows the relation between {\JobDescription}
attributes and the {\ExecutionTarget} attributes when the {\Broker}
base class filter the available targets to find those suitable for job
submission.

First, if the job description specifies submission to specific targets
and/or queues, the target will be checked and if it is not among these
targets and/or queues, it will be dropped. Next the number of free
slots on the target will be checked, and if no free slots exist, then
it will be dropped. After this, the health state of the target is
checked, and if any other value than "ok" is published then it is
dropped. Last, if middleware specific submission is specified in the
job description, the middleware type of the target is checked, and if
it does not satisfy the middleware requirements then it is
dropped. After these basic checks, certain attributes specified in the
job description are compared to the attributes published by the target
being processed. If the target does not publish a attribute which is
specified in the job description the target will dropped, with some
exceptions.
